%%%%%%%%%%%%%%%%%%%%%%%%
%% Sample use of the infthesis class to prepare a thesis. This can be used as 
%% a template to produce your own thesis.
%%
%% The title, abstract and so on are taken from Martin Reddy's csthesis class
%% documentation.
%%
%% MEF, October 2002
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%
%% Load the class. Put any options that you want here (see the documentation
%% for the list of options). The following are samples for each type of
%% thesis:
%%
%% Note: you can also specify any of the following options:
%%  logo: put a University of Edinburgh logo onto the title page
%%  frontabs: put the abstract onto the title page
%%  deptreport: produce a title page that fits into a Computer Science
%%      departmental cover [not sure if this actually works]
%%  singlespacing, fullspacing, doublespacing: choose line spacing
%%  oneside, twoside: specify a one-sided or two-sided thesis
%%  10pt, 11pt, 12pt: choose a font size
%%  centrechapter, leftchapter, rightchapter: alignment of chapter headings
%%  sansheadings, normalheadings: headings and captions in sans-serif
%%      (default) or in the same font as the rest of the thesis
%%  [no]listsintoc: put list of figures/tables in table of contents (default:
%%      not)
%%  romanprepages, plainprepages: number the preliminary pages with Roman
%%      numerals (default) or consecutively with the rest of the thesis
%%  parskip: don't indent paragraphs, put a blank line between instead
%%  abbrevs: define a list of useful abbreviations (see documentation)
%%  draft: produce a single-spaced, double-sided thesis with narrow margins
%%
%% For a PhD thesis -- you must also specify a research institute:
%\documentclass[phd,ilcc,twoside]{infthesis}

%% For an MPhil thesis -- also needs an institute
% \documentclass[mphil,ianc]{infthesis}

%% MSc by Research, which also needs an institute
% \documentclass[mscres,irr]{infthesis}

%% Taught MSc -- specify a particular degree instead. If none is specified,
%% "MSc in Informatics" is used.
% \documentclass[msc,cogsci]{infthesis}
 \documentclass[msc, ai, logo, 11pt]{infthesis}  % for the MSc in Informatics


%% Master of Informatics (5 year degree)
% \documentclass[minf]{infthesis}

%% Undergraduate project -- specify the degree course and project type
%% separately
% \documentclass[bsc]{infthesis}
% \course{Artificial Intelligence and Psychology}
% \project{Fourth Year Project Report}

%% Put any \usepackage commands you want to use right here; the following is 
%% an example:
\usepackage[sort, numbers]{natbib}
\usepackage{url}
%% Information about the title, etc.
\title{BRISK-based Visual Landmark Localisation using Nao Humanoid Robots}
\author{Daniel Mankowitz}


%% If the year of submission is not the current year, uncomment this line and 
%% specify it here:
% \submityear{1785}

%% Optionally, specify the graduation month and year:
% \graduationdate{February 1786}

%% Specify the abstract here.
\abstract{%
This thesis compares five feature extraction algorithms in order to determine the best algorithm to be implemented on a Nao humanoid robot for the purpose of localisation. The immediate application of this method is Robocup. The feature extraction algorithms include 1D SURF that has been developed by the \textit{rUNSWift} Robocup team \cite{Anderson} as well as BRISK-based techniques \cite{Leutenegger2011}. A novel scoring function has been developed in order to find the optimal parameters for the BRISK-based algorithms. Using these parameters BRISK0 - U-BRISK, a variation of BRISK, has been utilised, producing the best overall performance of all the algorithms. In the best case scenario it can match image pairs that overlap one another $90\%$ of the time without matching image pairs that do not overlap. This method can match Nao image pairs under varying illumination and can achieve reasonable matching performance when matching Nao images with those captured by a Nikon camera. A key result is that this method has been able to match a Nao's camera images with Google Street View images (albeit with decreased performance) which suggests that street navigation with the Nao may be possible. In addition, a novel constraint has been developed to remove invalid interest point matches in images. A new interest point property has also been created that may be used for the same purpose. Finally, a localisation algorithm that incorporates the BRISK0 U-BRISK feature extraction algorithm has also been developed for Robocup. This enables the Nao to efficiently determine its location on the football field.\\
}

%% Now we start with the actual document.
\begin{document}

%% First, the preliminary pages
\begin{preliminary}

%% This creates the title page
\maketitle

%% Acknowledgements
\begin{acknowledgements}
I would like to extend a huge thank you to my supervisor, Dr. Subramanian Ramamoorthy, for his incredibly helpful advice and useful insight that guided me in the right direction, resulting in a successful thesis. In addition I would like to thank Benjamin Rosman for his great ideas and useful feedback which were very helpful in developing my thesis. Aris Valtazanos was instrumental in helping me gain an excellent understanding of the Nao robot. Efstathios Vafeias gave me very useful insight into the inner-workings of feature extraction algorithms and the Nao's localisation module. I am also really grateful to Stephen McDonagh for his helpful feedback and useful comments.\\
\end{acknowledgements}

%% Next we need to have the declaration.
\standarddeclaration

%% Finally, a dedication (this is optional -- uncomment the following line if
%% you want one).
% \dedication{To my mummy.}

%% Create the table of contents
\tableofcontents

%% If you want a list of figures or tables, uncomment the appropriate line(s)
 \listoffigures
 \listoftables

\end{preliminary}

%%%%%%%%
%% Include your chapter files here. See the sample chapter file for the basic
%% format.

\include{introduction}
\include{background}
\include{robocup_feature_extraction_techniques}
\include{feature_matching}
\include{localisation}
\include{experiments_and_results}
\include{discussion_and_conclusion}
% \include{chap2}
%% ... etc ...

%%%%%%%%
%% Any appendices should go here. The appendix files should look just like the
%% chapter files.
\appendix
\include{appendix1}
%% ... etc...

%% Choose your favourite bibliography style here.
\bibliographystyle{apalike}

%% If you want the bibliography single-spaced (which is allowed), uncomment
%% the next line.
% \singlespace

%% Specify the bibliography file. Default is thesis.bib.
\bibliography{thesis.bib}

%% ... that's all, folks!
\end{document}
